|

### 2023-01-31 paper.Rmd
autogit

Unfortunately, as shown in figure \@ref(fig:airfoil-runtime-total), for the experiment conducted on the airfoil dataset with 2 hidden layers a negative impact of pre-training can be observed for the DAE-GP runtime.

>>>>

Unfortunately, as shown in figure \@ref(fig:airfoil-runtime-total), for the experiment conducted on the airfoil dataset with 2 hidden layers a strong negative impact of pre-training can be observed for the median runtime of DAE-GP. If the time spend on pre-training is included into the total runtime, the median duration for pre-trained DAE-GP over all 10 runs is $14706.465$ seconds as opposed to regular DAE-GP that has a median runtime of $5076.448. Even if the time spend
